### 2016-06-10 sec6_spm.tex
Further changes
Also reorganizing

\section{Star Partition and Mining}
\label{sec:spm_solution}
In order to achieve a good parallelism 
under any pattern parameters, we propose 
the \emph{Star Partition and Mining} (SPM) method. 
In SPM, we first design a novel object-based partition 
method named \emph{star partition}. Then, we adapt
an \emph{Apriori} method to mine GCMP patterns
out of each partition.

 The overview of the SPM method 
is presented in Algorithm~\ref{algo:spm_overview}.
As shown, the SPM method takes three phases. 
In the map phase, objects from the same cluster forms object-object pairs. 
The object-object pairs are then paired up with the timestamp of 
the snapshot to form a triplet(lines~\ref{code:spm-map-start}-\ref{code:spm-map-end}). 
In the partition phase, triplets with the same leading object form a \emph{star} which will be explained shortly 
(lines~\ref{code:spm-shuffle-start}-\ref{code:spm-shuffle-end}).
Lastly in the reduce phase, patterns are mined from each star structure (lines~\ref{code:spm-reduce-start}-\ref{code:spm-reduce-end}).

@@

\subsection{Star Partition}
The intuition of the star partition is that, if two objects are part 
of the same pattern, they must belong to the same cluster at 
some snapshots. Therefore, we may link objects that belong to the same cluster to form a \emph{connection graph}. Objects that are
not connected surely fail to form a pattern. We may then
partition the connection graph based on vertex connectivity
s.t. mining GCMPs can be done in parallel. We define the \emph{connection graph} and \emph{star}
as follows:
\begin{definition}[Connection Graph and Star]
A connection graph is an undirected graph $G=(V:E)$, where 
each $v \in V$ represents an object. An edge $e(s,t)= ET \in E$ 
contains all the timestamps at which $s,t$ are in the same cluster,
i.e., $\forall t \in ET, C_t(s) = C_t(t)$. 
A star of a vertex $s$, denoted as $Sr_s$, is the set of incidental edges on $s$ whose
another ending vertex is greater than $s$. I.e, $\forall e(s,t) \in Sr_s$, $s < t$. We name $s$
as the \emph{central vertex} of $Sr_s$.
\end{definition}

It is notable that we require vertices in a star to be greater than its central vertex. This 
effectively avoids replicating edges. \emph{Connection graph} and \emph{star} examples are 
shown in Figure~\ref{fig:star_partition} (a) and (b). In (a), a connection graph is formed
based on the example in Figure~\ref{fig:related_work}.
In (b), 5 stars are presented. It is easy to see that, by requiring the center vertex to be
the smallest vertex in a star, there are no edges been replicated. In implementation,
as stated in Algorithm~\ref{algo:spm_overview} line~\ref{code:spm-edge-direct}, the
comparison between vertices/objects are based on the vertex/object ID.

@@

%After computing the star, each partition is applied with a reduce task. 
%Indeed, a star $Sr_s$ can be viewed as a subset of original trajectories. 
%This is done by treating each vertex in $Sr_s$ as an object. 
%The time sequence of $s$ is the union of all edges in $Sr_s$. 
%And the time sequence of $v \neq s$ is the edge $(s,v)$. Therefore, we
%are able to mine stars from the similar trajectory concepts.
Although star partition is performed based on the object connections, each star
can be effectively viewed as a subset of trajectories. To see this, each vertex
in a star can be viewed as an object. The timestamps of center vertex $s$ is the
union of all the edges in $Sr_s$. The timestamps of vertex $v \neq s$ is the 
edge $e(s,v)$. Therefore, we are able to define and mine GCMP on the stars. 
Before describing the mining strategy, we first state in the following theorem that 
the star-partition is complete and sound:
\begin{theorem}[Soundness and Completeness of Star Partition]
Star partition is sound and complete.
\end{theorem}

\begin{proof}
For the soundness,
if $P$ is a valid pattern in $Sr_s$, then at every time $t$, $\forall o_1, o_2 \in P.O$, $C_t(o_1) = C_t(o_2)$.
By definition, $P$ is valid in the original trajectories.
For the completeness,
if $P$ is a valid pattern in original trajectories, let $s$ be the object with smallest ID in $P.O$. 
Then by the definition of pattern, $\forall t \in P.T$, $\forall o \in P.O$, $C_t(s) = C_t(o)$.
It follows that all object $o \in P.O$ are in $Sr_s$. Furthermore, every timestamp in $P.T$ is included
in $Sr_s$. Therefore, $P$ is a valid pattern in $Sr_s$.
\end{proof}

Based on the above theorem, we can mine GCMP from each partition independently.
It is notable that, in star partition, original data is replicated for $O(|\mathbb{O}|)$ times
as each object may be sent to $O(|\mathbb{O}|)$ partitions. Since this complexity is free
from pattern parameters, the star partition is more scalable than the temporal replication.
In later sections, we will describe several engineering level optimization to further reduce the amount of replicated data.

\subsection{Apriori Mining}
In the mining phase, we need to find the patterns within each star. 
To systematically discover the patterns, we design the \emph{Apriori Mining} method which
is similar to the technique in frequent item mining literature. During the algorithm, we call a candidate pattern $R$-pattern if the size of its object set is $R$. 
Our algorithm runs in iterations. During each iteration $R$, we try to generate all $(R+1)$-patterns. In iteration $1$, the $2$-pattern is the edges in $Sr_s$. In particular,
for each $e(s,v)=ET$, pattern $p=(\{s,v\}, ET)$ is formed. During each iteration, 
we generate $(R+1)$-patterns by joining $R$-patterns with $2$-patterns. Specifically,
the join between $p_1=(O_1:T_1)$ and $p_2=(O_2:T_2)$ would generate a new pattern $p_3=(O_1 \cup O_2:T_1 \cap T_2)$. Notice that in $Sr_s$, each $R$-pattern consists of the object $s$, thus the join will grow a $R$-pattern at most to a $(R+1)$-pattern.
Our mining algorithm stops where no further patterns are generated. The algorithm is illustrated as in Algorithm~\ref{algo:apriori_mining}.

@@

It is notable that Algorithm~\ref{algo:apriori_mining} takes exponential complexity to mine GCMP. There
are two major factors dragging down the performance. First, the size of $Sr_s$ affects
the initial size of $2$-patterns. Second, the candidates generated in each level affects the join performance. In later
sections, we exploit the property of GCMP to reduce the two factors.

>>>>

\section{Star Partition and Mining}
\label{sec:spm_solution}
TRM approach requires to replicate entire
trajectories $O(|\mathbb{T}|)$ times, which is inefficient
in parallelism. To overcome this limitation, we 
propose the \emph{Star Partition and Mining} (SPM) method.
In SPM, we design a graph model, named \emph{connection graph}, to capture 
the co-moving behavior among objects. In such a way, 
given an object $u$, all the objects potentially
co-moved with $u$ are captured in $u$'s neighborhood, which
forms a \emph{star} structure in graph terms. SPM utilizes
such structures to partition objects and then adapts an Apriori 
algorithm to discover true GCMPs from each partition.

The flow of SPM method is presented in Figure~\ref{fig:star_partition}.
SPM utilizes the same preprocessing as TRM, thus the flow starts
from clusters in each snapshot. Conceptually, the clusters 
in each snapshot forms a graph as shown in Figure~\ref{fig:star_partition} (a).
In the map phase of \emph{SPM}, a vertex together with its neighborhood 
vertexes form a star. Every star is indeed an independent partition.
Then, stars are shuffled to reducers. As in
Figure~\ref{fig:star_partition} (c), Apriori mining algorithm is adapted
to mine the GCMP patterns. The overview implementation of SPM is shown 
in Algorithm~\ref{algo:spm_overview}.

%The overview of the SPM method is presented in 
%Algorithm~\ref{algo:spm_overview}. As shown, SPM takes three phases. 
%In the map phase, objects from the same cluster form object-object pairs. 
%The object-object pairs are then paired up with the timestamp of 
%the snapshot to form a triplet(lines~\ref{code:spm-map-start}-\ref{code:spm-map-end}). 
%In the partition phase, triplets with the same leading object form a \emph{star} which will be explained shortly 
%(lines~\ref{code:spm-shuffle-start}-\ref{code:spm-shuffle-end}).
%Lastly in the reduce phase, patterns are mined from each star structure (lines~\ref{code:spm-reduce-start}-\ref{code:spm-reduce-end}).

@@

\subsection{Star Partition}
The intuition of the star partition is that, if two objects are part 
of the same pattern, they must belong to the same cluster at 
those snapshots. Therefore, we may link objects that belong to 
the same cluster to form the \emph{connection graph}. Objects that are
not connected surely fail to form a pattern. We may then
partition the connection graph based on vertex connectivity
such that mining GCMPs can be done in parallel. 
We formally define the \emph{connection graph} as follows:
\begin{definition}[Connection Graph]
A connection graph is an undirected graph $G=(V:E)$, where 
each $v \in V$ represents an object. An edge $e(s,t)= ET \in E$ 
contains the timestamp sequence at which $s,t$ are in the same cluster,
i.e., $\forall t \in ET, C_t(s) = C_t(t)$. 
\end{definition}

In graph theory, a \emph{star} of a vertex $u$ is the
the set of neighborhood vertexes of $u$. To utilize \emph{star}
partition, since a vertex may appear in multiple stars, 
some replications of vertexes are required. In order to avoid replication 
of edges, we use the \emph{directed star} as follows:

\begin{definition}[Directed Star]
Assign each vertex in $G$ an ID, a direct star of a vertex $s$, denoted as $Sr_s$, 
is the set of incidental edges on $s$
such that $\forall e(s,t) \in Sr_s$, $s < t$. We name $s$
as the \emph{central vertex} of $Sr_s$.
\end{definition}

By leveraging the \emph{directed star}, we avoids replicating the edges. 
A \emph{Connection graph} and \emph{star} examples are 
shown in Figure~\ref{fig:star_partition} (a) and (b). In (a), a connection graph is formed
based on the example in Figure~\ref{fig:related_work}.
In (b), 5 stars are presented. It can be figured out that by leveraging directed star, 
no edges are replicated. In implementation,
as show in Algorithm~\ref{algo:spm_overview} line~\ref{code:spm-edge-direct}, the
comparison between vertices/objects are based on the vertex/object IDs.

@@

%After computing the star, each partition is applied with a reduce task. 
%Indeed, a star $Sr_s$ can be viewed as a subset of original trajectories. 
%This is done by treating each vertex in $Sr_s$ as an object. 
%The time sequence of $s$ is the union of all edges in $Sr_s$. 
%And the time sequence of $v \neq s$ is the edge $(s,v)$. Therefore, we
%are able to mine stars from the similar trajectory concepts.

\subsection{Apriori Mining}
To systematically discover valid patterns in each star, 
we design the \emph{Apriori Mining} algorithm. 
To describe the  algorithm, we call a candidate pattern $R$-pattern 
if the size of its object set is $R$.  Therefore, each edge
in the star is effectively a $2$-pattern. The intuition of Apriori mining
is the observation that $(R+1)$-patterns can be generated
from $R$-patterns and $2$ patterns. Thus, we may iteratively 
enumerate pattern candidates with all possible sizes.
In particular, initially, for each $e(s,v)=ET$, pattern $p=(\{s,v\}, ET)$ is formed. 
During each iteration, we generate $(R+1)$-patterns by joining $R$-patterns 
with the $2$-patterns. Technically, the join between $p_1=(O_1:T_1)$ and $p_2=(O_2:T_2)$
generates a new pattern $p_3=(O_1 \cup O_2:T_1 \cap T_2)$. Note that in $Sr_s$,
each $R$-pattern contains the object $s$, thus the join only 
grow a $R$-pattern at most to a $(R+1)$-pattern.
Our mining algorithm stops where no further patterns are generated. 
The algorithm is illustrated as in Algorithm~\ref{algo:apriori_mining}.

@@

It is notable that, in star partition, original data is 
replicated for $O(|\mathbb{O}|)$ times as each object may 
be sent to $O(|\mathbb{O}|)$ stars. Since in reality, $|\mathbb{T}| \gg |\mathbb{O}|$, 
the star partition is more scalable than the temporal replication.
In later sections, we will describe several engineering level optimization to further reduce the amount of replicated data.
%It is notable that Algorithm~\ref{algo:apriori_mining} takes exponential
%time to mine GCMP. There are two major factors dragging 
%down the performance. First, the size of $Sr_s$ affects the initial 
%size of $2$-patterns. Second, the candidates generated in each 
%level affects the join performance. In later
%sections, we exploit some properties of GCMP to reduce the two factors.

\subsection{Analysis of SPM}
The analysis of SPM contains two parts. We first prove the correctness
of SPM. Then, we analyze the work load distribution of the star sizes.

\subsubsection{Correctness}
Although star partition is performed based on the connection graph, 
each star is indeed a projection of original trajectories.
To see this, each vertex can be viewed as an object. 
The timestamps of center vertex $s$ is the union of all the 
edges in $Sr_s$. The timestamps of vertex $v \neq s$ is the 
edge $e(s,v)$. Therefore, stars can be viewed as a trajectory
database, where GCMP can be similarly defined. Using the same 
notions as Definition 4, we state the correctness
of star partition as follows:

\begin{theorem}[Soundness and Completeness of Star Partition]
Star partition is sound and complete.
\end{theorem}

\begin{proof}
For the soundness,
if $P$ is a valid pattern in $Sr_s$, then at every time $t$, 
$\forall o_1, o_2 \in P.O$, $C_t(o_1) = C_t(o_2)$.
By definition, $P$ is valid in the original trajectories.
For the completeness,
if $P$ is a valid pattern in original trajectories, 
let $s$ be the object with smallest ID in $P.O$. 
Based on the definition of GCMP, $\forall t \in P.T$, $\forall o \in P.O$, $C_t(s) = C_t(o)$.
It follows that all object $o \in P.O$ are in $Sr_s$. 
Furthermore, every timestamp in $P.T$ is included
in $Sr_s$. Therefore, $P$ is a valid pattern in $Sr_s$.
\end{proof}

\subsubsection{Optimal Star Partition}
An important concern in design parallel algorithms is 
the distribution of work loads. Unlike TRM where each partition
contains equal-sized snapshot, the size distribution 
of stars remains SPM unknown. 
Traditionally, the quality of a partition strategy 
is measured based on two aspects: (1) the number of result partition, which
affects the maximum parallelism
(2) the balance of partition sizes, which affects the finishing
time of a job. We notice that, in star partition, the total sizes of 
stars are invariant. Therefore, the quality of a partition strategy
can be formalized as the \emph{skewness}, which is the maximum star size
among all stars. Smaller \emph{skewness} naturally results in more partitions
and less imbalance.

\begin{figure}[h]
\centering
\includegraphics[width=0.4\textwidth]{star-alt.eps}
\caption{An alternative numbering and partitioning of the connection graph in Figure~\ref{fig:star_partition}.}
\label{fig:star-alt}
\end{figure}

Interestingly, we note that the \emph{skewness} of star partition is affected by
the way the vertexes are numbered in the connection graph. For example,
Figure~\ref{fig:star-alt} gives two valid numbering of vertexes 
in the same connection graph, but produces two different set of stars. 
The upper partitioning constructs four stars with the maximum star consisting of 5 edges.
The lower partitioning constructs five stars with the maximum star consisting of 3 edges.
Apparently the upper partitioning is inferior because its \emph{skewness} is 5 while the
lower one's \emph{skewness} is 3.

Ideally we wish to find a numbering scheme of connection graph
that minimize the \emph{skewness}.
To quantify the objective, we design an linear algebra model as follows: Let $G$ denote a connection graph.
Let $\mathbb{A}$ be an arbitrary numbering of vertexes in $G$.
Let $(A:a_{i,j})$ be a boolean assignment matrix wrt. $\mathbb{A}$ (i.e., $a_{i,j}$ indicates whether vertex $j$ is included in $Sr_i$). Let vector $\vec{b}$
be the \textit{one}\footnote{Every element in $\vec{b}$ is $1$} vector. Let $\vec{c} = A\vec{b}$, then
each $c_i \in \vec{c}$ denotes the size of star for vertex $i$.
Therefore, minimizing the \emph{skewness} can be formulated as follows:
\begin{equation}
\mathbb{A}  = \argmin(||A\vec{b}||_\infty) \text{,where } ||A\vec{b}||_\infty = \max_{1\leq j \leq n}(c_j)
\end{equation}

It is challenging to directly optimize the above equation. 
First, suppose there are $n$ vertexes in $G$, enumerating
all possible $\mathbb{A}$s leads to $n!$ combinations. 
Such a high complexity is trivially unpractical. Second,
since $G$ is only conceptual at runtime, 
the load planning cannot be done beforehand. 
Despite these challenges, we observe that there is a 
$O(1)$ time solution which is good enough as stated in the 
following theorem.

\begin{theorem}[Balance of Star Partition]
Let $G$ be a connection graph with $n$ vertexes and the average degree $d$.
Let $\mathbb{A}^*$ be the optimal numbering wrt. Equation 1.
For any numbering, $\mathbb{A}$, with high probability, the 
absolute skewness difference between $\mathbb{A}^*$ and $\mathbb{A}$ is $O(\sqrt{n \log n})$.
That is, it is very likely that 
$||\mathbb{A}\vec{b}||_\infty = ||\mathbb{A}^*\vec{b}||_\infty + O(\sqrt{n \log n})$.
\end{theorem}

\begin{proof}
Let $\mathbb{A}^*$ be the optimal solution wrt Equation 1. Since we have a star
for each object, by the degree-sum formula and pigeon-hole theorem, $||A^*\vec{b}||_\infty \geq d/2$.
Next, let $e_{i,j}$ be an entry in the adjacent matrix of $G$. Note that edges in $G$ are independent. 
Let $d_i$ denote the degree of vertex $i$ in $G$. 
It follows that $E[d_i]=E[\Sigma_{1\leq j \leq n}e_{i,j}]=d$.
Since in the star partition, each edge is assigned to the vertex
with smaller IDs, the connection between $a_{i,j}$ and $e_{i,j}$ can be written as:
\begin{equation*}
a_{i,j} = \begin{cases}
			e_{i,j}, i>j \\
			0, otherwise
		  \end{cases}  
\end{equation*}
There are two observations made on the above equation. First, since $e_{i,j}$s are independent,
$a_{i,j}$s are independent. Second, since $i>j$ and $e_{i,j}$ are independent. 
$E[a_{i,j}] = E[e_{i,j}]E[i>j]= E[e_{i,j}]/2$.

By definition, $c_i = \Sigma_{1\leq j \leq n} a_{i,j}$, 
is a sum of $n$ independent 0-1 variables. Taking expectation on both sides, 
we get: $E[c_i] = E[\Sigma_{1\leq j \leq n} a_{i,j}]=E[\Sigma_{1\leq j \leq n} e_{i,j}]/2 = d/2$. Let $\mu =E[c_i] = d/2$, 
$t = \sqrt{n\log n}$, by Hoeffding's Inequality, the following holds:
\begin{equation*}
\begin{split}
	Pr(c_i \geq \mu + t) 
						&\leq \exp(\frac{-2t^2}{n}) \\
						&= \exp(-2\log n) = n^{-2}
\end{split}
\end{equation*}

The first step is due to the fact that all $a_{i,j}$ are bounded in the range of [0,1]. 
Next, since the event $(\max_{1\leq j \leq n}(c_j) \geq \mu + t)$ can be viewed as
$\cup_{c_i} (c_i \geq \mu + t )$, by Union Bound, we achieve the following:
\begin{equation*}
\begin{split}
	Pr(||A\vec{b}||_\infty \geq \mu + t) &=Pr(\max_{1\leq j \leq n}(c_j) \geq \mu + t)  \\
		& = Pr(\cup_{c_i} (c_i \geq \mu + t )) \\
		&\leq \Sigma_{1 \leq i \leq n} Pr(c_i \geq \mu + t) \\
		& = n^{-1} = 1/n
\end{split}
\end{equation*}
Substitute $t$ and $\mu$, we achieve the following concise form:
\begin{equation*}
	Pr(||A\vec{b}||_\infty \geq (d/2 + \sqrt{n\log n})) \leq 1/n
\end{equation*}
This indicates that, the probability of $(||A\vec{b}||_\infty-d/2)$ being less than or equal to $ O(\sqrt{n\log n})$ is $(1-1/n)$. With the observed fact that $||A^*\vec{b}||_\infty \geq d/2$, we conclude that
with probability greater than $(1-1/n)$, 
the difference between $||A\vec{b}||_\infty$ and $||A^*\vec{b}||_\infty$ is less than $O(\sqrt{n\log n})$.
\end{proof}

In fact, we have a tighter bound of $||A\vec{b}||_\infty -||A^*\vec{b}||_\infty$ if 
the connection graph is \emph{dense}. Specifically, if $d\geq \sqrt{12\log n}$, the following
equation holds:
\begin{equation*}
Pr(||A\vec{b}||_\infty \geq (d/2 + O(\sqrt{d\log n})) \leq 1/n
\end{equation*}

### 2016-06-10 sec7_optimization.tex
Some revisement
Section 4, Section 5 needs to merge
Further changes
Also reorganizing

\section{Optimization}
\label{sec:optimization}
In this section, we describe several optimizations to the star-partition and mining algorithm.
In addition, we also address some practical issues when deploying the SPM algorithm
to real MapReduce based systems.

%We have analyzed that the bottlenecks of Algorithm~\ref{algo:apriori_mining} 
%lies in two factors. The size of each $Sr_s$ and the size of candidates in each level of Apriori.
%In this section, we provide several optimizations to boost the bottlenecks.
%\subsection{Edge Reduction by Direction}
%The first spot for reducing the size of $Sr_s$ is to remove the replicated edges. As shown in Algorithm~\ref{algo:spm_overview}, each edge in the conceptual graph is replicated twice in generating the star-structure. The purpose of replication is to ensure the completeness of star partition. However, this replication can be avoided if we choose an appropriate way of partitioning. 
%
%We design the edge partitioning method by edge direction. Instead of building a conceptual graph that is undirected, we create the directed conceptual graph as follows: First, we assign each object a unique number. Then
%for a cluster $C_t$ in snapshot $S_t$, for any pair $(u,v) \in C_t$, an edge $e(u,v) = \{t\}$ is created if $u < v$. It is easy to see that the directed conceptual graph is a DAG. We then create each $Sr_u$ by including all the outgoing edges of $u$. By so doing, each edge is assigned to only one star, thus avoids the replications. We use the following theorem to ensure the completeness of the edge direction method.
%
%\begin{theorem}[Sound and Completeness of Edge Direction]
%Star partition with edge direction is sound and complete.
%\end{theorem}
%\begin{proof}
%It is notable that each star is a subset of original trajectories, thus the soundness is trivially true. For completeness, if $P$ is valid pattern, then let $s$ be the object of the smallest number in $P.O$, i.e., $s=\min_{o \in P.O}(o)$. Since $s$ is smallest and the all other objects in $P.O$ is connected with $s$. Therefore, $P.O \equiv Sr_s$, which indicates that $P.O$ is also a pattern in $Sr_s$.
%\end{proof}
%An example of edge direction is shown in Figure~\ref{fig:star_partition}. As shown,
%by adapting the direction method, half the size of $S_r$'s is reduced. This clearly brings efficiency in both shuffling and apriori mining.

@@

\subsection{Candidate Pruning}
\subsubsection{Temporal monotonicity}
During the apriori phase, we repeatedly join candidate patterns in different levels to generate a larger set
of a patterns. We observe that traditional monotonic property of Apriori algorithms \textbf{does not}
hold in GCMP mining. That is given two candidate $P_1, P_2$, if $P_1.O \subset P_2.O$ and $P_1$ is not 
a valid pattern, then $P_2$ may or may not be a valid pattern. However, we notice that
we may form another monotonic property based on the \emph{candidate sequence} such that
the Apriori algorithm could still benefit.

@@

\subsubsection{Forward closure checking}

\begin{example}
We use Figure~\ref{fig:star_partition} (c) to demonstrate the candidate pruning. As shown, at the initial stage, $\{3,6:1,4\}$ is pruned, since $\{1,4\}$ is not a candidate sequence. By temporal monotonicity, candidates containing objects $\{3,6\}$ can all be pruned. Therefore, we are able to directly prune $\{3,4,6\}$, $\{3,5,6\}$ and $\{3,4,5,6\}$.
\end{example}
%
%With the help of the \emph{Monotonic Property}, the number of new candidates in each level is greatly reduced. We verify this in the experiment session as well.
\subsection{Load Balancing}

\subsection{Duplication Detection}

\subsection{Handling Overlapping Clusters}

>>>>

\section{Optimizing SPM}
\label{sec:optimization}
It is notable that Algorithm~\ref{algo:apriori_mining} takes exponential
time to mine GCMP. There are two major factors dragging 
down the performance. First, the size of $Sr_s$ affects the initial 
size of $2$-patterns. Second, the candidates generated in each 
level affects the join performance.
In this section, we describe several practical techniques to boost the performance
of SPM.
%We have analyzed that the bottlenecks of Algorithm~\ref{algo:apriori_mining} 
%lies in two factors. The size of each $Sr_s$ and the size of candidates in each level of Apriori.
%In this section, we provide several optimizations to boost the bottlenecks.
%\subsection{Edge Reduction by Direction}
%The first spot for reducing the size of $Sr_s$ is to remove the replicated edges. As shown in Algorithm~\ref{algo:spm_overview}, each edge in the conceptual graph is replicated twice in generating the star-structure. The purpose of replication is to ensure the completeness of star partition. However, this replication can be avoided if we choose an appropriate way of partitioning. 
%
%We design the edge partitioning method by edge direction. Instead of building a conceptual graph that is undirected, we create the directed conceptual graph as follows: First, we assign each object a unique number. Then
%for a cluster $C_t$ in snapshot $S_t$, for any pair $(u,v) \in C_t$, an edge $e(u,v) = \{t\}$ is created if $u < v$. It is easy to see that the directed conceptual graph is a DAG. We then create each $Sr_u$ by including all the outgoing edges of $u$. By so doing, each edge is assigned to only one star, thus avoids the replications. We use the following theorem to ensure the completeness of the edge direction method.
%
%\begin{theorem}[Sound and Completeness of Edge Direction]
%Star partition with edge direction is sound and complete.
%\end{theorem}
%\begin{proof}
%It is notable that each star is a subset of original trajectories, thus the soundness is trivially true. For completeness, if $P$ is valid pattern, then let $s$ be the object of the smallest number in $P.O$, i.e., $s=\min_{o \in P.O}(o)$. Since $s$ is smallest and the all other objects in $P.O$ is connected with $s$. Therefore, $P.O \equiv Sr_s$, which indicates that $P.O$ is also a pattern in $Sr_s$.
%\end{proof}
%An example of edge direction is shown in Figure~\ref{fig:star_partition}. As shown,
%by adapting the direction method, half the size of $S_r$'s is reduced. This clearly brings efficiency in both shuffling and apriori mining.

@@

\subsection{Temporal monotonicity}
During the apriori phase, we repeatedly join candidate patterns in different levels to generate a larger set
of a patterns. We observe that traditional monotonic property of Apriori algorithms \textbf{does not}
hold in GCMP mining. That is given two candidate $P_1, P_2$, if $P_1.O \subset P_2.O$ and $P_1$ is not 
a valid pattern, then $P_2$ may or may not be a valid pattern. However, we notice that
we may form another monotonic property based on the \emph{candidate sequence} such that
the Apriori algorithm could still benefit.

@@

\subsection{Forward closure checking}
Although leveraging \emph{temporal monotonicity} could largely prune false candidates and reduce
the apriori search space, it is ineffective when a \textit{true} pattern exists. 
For example, if a final pattern of a star $Sr_s$ is the \textit{union of all vertices} in the star, 
then in apriori, ${|Sr_s|}\choose{i + 1}$ candidates needs to be generated at 
each level $i$. This results in an exponential search space while
the output only contains one pattern.  
In general, when candidates at level $i$ collectively forms a true pattern, 
running aprior produces many wasted candidates.

Let $Lv_i$ be the set of candidates at level $i$ of Algorithm~\ref{algo:apriori_mining},
we use the \emph{forward closure} $FC_i$ to denote the union of the objects in
all candidates in $Lv_i$. Then, the \emph{forward closure checking} is stated as follows:
\begin{theorem}[Forward Closure Checking Rule]
Let $Lv_i$ be the candidates generated at level $i$ in Algorithm~\ref{algo:apriori_mining},
if $FC_i$ is a proper pattern, then it is safe to terminate Algorithm~\ref{algo:apriori_mining}
and directly output $FC_i$.
\end{theorem}

\begin{proof}
We prove by contradiction. Suppose there exists another pattern $P$ such that $P.O \neq FC_i$, let 
$X=P.O - FC_i \neq \emptyset$. Consider a subset of $P$ which contains $X$ with size $i+1$, (i.e., $P_1 \subseteq P, P_1\subseteq X, |P_1|=i+1$). Since $P$ is a proper pattern, then $P_1$ is also a proper pattern. Therefore $P_1 \in Lv_i$.
Then it follows $X$ is in the forward closure of $FC_i$, (i.e.,$X \in FC_i$), which contradicts with $X\notin FC_i$.
\end{proof}

It is notable that, as the level grows in Algorithm~\ref{algo:apriori_mining}, the closure $FC$
reduces, thus the pruning power of $FC$ would be stronger.

%To facilitate efficient mining, we adapt the \emph{forward closure checking} rule to 
%quickly determine whether it is sufficient to terminate the apriori search. Given the candidates at
%level $i$ $Lv_i$, we define the \emph{forward closure} of $Lv_i$ as the union of objects from
%all candidates. Then, the following \emph{forward closure checking} rule can be used:
%
%\begin{theorem}[Forward Closure Checking Rule]
%Let $Lv_i$ be the candidates generated at level $i$ in Algorithm~\ref{algo:apriori_mining}, the forward closure
%is $\mathbb{F}_i = \cup_{cand \in Lv_i} (cand.O) $. Algorithm~\ref{algo:apriori_mining} terminates when 
%$FC_i$ forms a valid GCMP .
%\end{theorem}

\begin{example}
We use Figure~\ref{fig:star_partition} (c) to 
demonstrate the power of candidate pruning. 
As shown, at the initial stage, $\{3,6:3\}$ is first pruned by \textit{Edge Simplification} since its
timestamps fails to be a candidate sequence. Subsequently, all further candidates containing $\{3,6\}$ 
are pruned by \textit{Temporal Monotonicity}. Then, we check the \textit{Forward Closure} 
of remaining candidates (i.e., $\{3,4\}$ and $\{3,5\}$) and find $\{3,4,5\}$ is a
valid candidate. Therefore, $\{3,4\}$ and $\{3,5\}$ are pruned, and $\{3,4,5\}$ is the output.
\end{example}
%
%With the help of the \emph{Monotonic Property}, the number of new candidates in each level is greatly reduced. We verify this in the experiment session as well.

Induced by the Theorem 5, taking object IDs as the numbering (i.e., in Algorithm~\ref{algo:spm_overview})
would be guaranteed to produce a partition which is almost optimal.
%By definition, $c_i = \Sigma_{1\leq j \leq n} a_{i,j}$, is a sum of $n$ independent 0-1 variables.
%Taking expectation on both sides, we get: $E[c_i] = E[\Sigma_{1\leq j \leq n} a_{i,j}]=E[\Sigma_{1\leq j \leq n} e_{i,j}]/2 = d/2$. Let $\mu =E[c_i] = d/2$, $\delta = \sqrt{12\log n/d}$, by Chernoff Bound, 
%the following holds:
%\begin{equation*}
%\begin{split}
%	Pr(c_i \geq (1+ \delta)\mu) & \leq \exp(-\mu \delta^2 / 3) \\
%						&= \exp(-d/2 \times 12 \log n / 3d ) \\
%						&= \exp(-2\log n) = n^{-2}
%\end{split}
%\end{equation*}
%
%Next, since the event $\max_{1\leq j \leq n}(c_j) > (1+ \delta)\mu$ can be viewed as
%$\cup_{c_i} (c_i > (1+ \delta)\mu )$, by Union Bound, we achieve the following:
%\begin{equation*}
%\begin{split}
%	Pr(||A\vec{b}||_\infty > (1+ \delta)\mu)) &=Pr(\max_{1\leq j \leq n}(c_j) > (1+ \delta)\mu)  \\
%		&\leq \Sigma_{1 \leq i \leq n} Pr(c_i \geq (1+ \delta)\mu) \\
%		& = n^{-1} = 1/n
%\end{split}
%\end{equation*}
%Substitute $\mu$ and $\delta$, we achieve the following concise form:
%\begin{equation*}
%	Pr(||A\vec{b}||_\infty > (d/2 + \sqrt{3 d\log n})) \leq 1/n
%\end{equation*}
%This indicates that, the probability of $(||A\vec{b}||_\infty-d/2)$ being less than $ O(\sqrt{d\log n})$ is $(1-1/n)$. Notice that $||A^*\vec{b}||_\infty \geq d/2$, therefore, with probability greater than $(1-1/n)$, the difference between $||A\vec{b}||_\infty$ and $||A^*\vec{b}||_\infty$ is less than $O(\sqrt{d\log n})$.
%\end{proof} 
%
%Theorem 5 is powerful enough to induce the following lemma:
%\begin{theorem}[Load Balance of Algorithm~\ref{algo:spm_overview}]
%The partitioning in Algorithm~\ref{algo:spm_overview} differs at most $O(\sqrt{d\log |\mathbb{O}|})$ 
%from optimal partitioning with probability $(1-1/|\mathbb{O}|)$.
%\end{theorem}
